Glyph-maps for Visualizing Climate Data and Models

### 2011-09-28 paper.tex
re-done fig 7, order of names

\title{Glyph-maps for Visualizing Climate Data and Models}
\author{Dianne Cook$^1$, Heike Hofmann$^1$, Charlotte Wickham$^2$, Hadley Wickham$^3$, \\
$^1$Department of Statistics, Iowa State University\\
$^2$ Department of Statistics, Oregon State University\\
$^3$ Department of Statistics, Rice University}
\date{}

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.33\linewidth]{month-rescale01-col}
 \caption{Adding colour to scaled plots. Here each location has been scaled to range $[0, 1]$ and colour mapped to the range of the original predictions. Pale locations have smaller range than darker locations. Shapes at all locations are visible, but attention is drawn to locations with larger ranges.}
 \label{fig:scaling-col}
\end{figure}

>>>>

\title{Glyph-maps for Visualizing Climate Data and Models}
\author{Hadley Wickham$^1$, Heike Hofmann$^2$, Charlotte Wickham$^2$, Dianne Cook$^2$\\
$^1$ Department of Statistics, Rice University}
$^2$Department of Statistics, Iowa State University\\
$^3$ Department of Statistics, Oregon State University\\
\date{}

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.5\linewidth]{month-rescale01-col}%
 \includegraphics[width=0.5\linewidth]{month-rescale01-fill}
 \caption{Adding colour to scaled plots. Here each location has been scaled to range $[0, 1]$ and colour mapped to the range of the original predictions. Pale locations have smaller range than darker locations. Shapes at all locations are visible, but attention is drawn to locations with larger ranges.}
 \label{fig:scaling-col}
\end{figure}
